InteroceptionStudy_GPValidation

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
Update IAPS_PREPROCESSING_2021_1.Rmd

# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)
```

@@

```{r}
tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))

@@

>>>>

# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)

colnames(tmp.df4_sum_full)
```

@@

# add the self report
```{r}

View(tmp.df4_sum_full_bio_hr)

library(readxl)
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")

View(db_selfrep)
db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")

db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)

tmp.df4_sum_full_bio_hr$ssid <- as.character(tmp.df4_sum_full_bio_hr$ssid)

tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')

write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')

@@

merge parsed data
```{r}
tmp.df4_sum_full_bio_hr_self
db_parsed_summarised2$ssid<- as.character(db_parsed_summarised2$ssid)

tmp.df4_sum_full_bio_hr_self_parsed <- left_join(tmp.df4_sum_full_bio_hr_self, db_parsed_summarised2, 
                             by = c("ssid", "trialUnq", "tNo", "screencontent"))

# tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))

# save the timecourse data and the aggregated data

tmp.df4_sum_full_bio_hr_self_parsed
write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
```
